Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-07-04 WRITEUP/ms.tex
minor fix and wording edits with AF

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization using cosmological zoom-in simulation.
We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') 
using an H$_2$ density-based clump finder. 
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter to \obs and perform Toomre-Q stability 
analysis to understand the origin and dynamical properties of MCC.
%
In \flower, the typical MCC mass is $10^{6.5}$\,\Msun, with sizes $R\simeq45-100$\,pc, 
which are comparable to nearby spirals and starburst galaxies. 
MCCs are highly supersonic and supported by non-thermal turbulence, with velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way).
That said, their velocity dispersion and gas surface density are comparable to nearby and $z$\ssim2 gas-rich starburst galaxies.
%
We identify gravitationally unstable MCCs via Toomre $Q_{\rm eff}$ analysis and
the more observationally accessible virial parameter ($\alpha_{\rm vir}$) analysis.
MCCs in the main disk of \flower are globally stable. MCCs in the densest regions have lower $\alpha_{\rm vir}$ 
and $Q_{\rm eff}$ values, % indicative of instability to collapse. 
where star formation is expected to take place within the clumps and cores on even smaller scales, as non-thermal energy 
quickly dissipates. % and the gas structures are no longer supported by turbulence.
%
As such, detailed studies on the star-forming gas dynamics at EoR requires a spatial resolution of $\lesssim$40\,pc, which is 
within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\subsection{Larson's Relations and Virial Parameter}\label{sec:PVE}

@@

\subsection{Toomre stability analysis}\label{sec:Q}

The onset of gravitational instability is tightly connected to \SF
%mm2 [added Martin & Kennicutt 2001]
\citep[e.g.,][]{Kennicutt89a, Martin01, Wang94a, Li05b, Li06a}. For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma_{\rm disk}^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{\altomega}\frac{d}{d\altomega}\left(\altomega^2\Omega\right)\,.
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a}.
In Equation~\ref{eqn:3Ddisp} the terms on the right hand side are related to rotation, self-gravity and internal pressure, respectively. Heuristically, the instability can be understood by considering the scale at which gravitational potential overcomes the internal energy. Gravity dominates at scales $L > L_J$, where $L_J$ is the Jeans length. However, differential rotation in disk galaxies can stabilize perturbations that might otherwise collapse for $L > L_{\rm rot}$, where $L_{\rm rot}$ is set by $\kappa$. As a result, disks are unstable to gravitational collapse on scales between $L_J < L < L_{\rm rot}$.

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MCCs identified in \flower by our clump finder.
%
The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
%
Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
%
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
%
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel. \AP{please change $\rm Kpc$ to $\rm kpc$}
\label{fig:MCC}
}
\end{figure*}

@@

\subsection{Molecular Cloud Complex Properties} \label{sec:distribution}

@@

\subsection{Distributions of MCC Basic Properties
  % mm2 and Outlier
} \label{sec:dist}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\AP{please change $M_{\rm cl}$ into $M_{\rm gas}$}
\label{fig:dist}}
\end{figure*}

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussions}\label{sec:diss}

\subsection{Comparing MCC Observable Quantities to Observations} \label{sec:diss1}

@@

The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges between $\log(P/k_B \,{\rm K}\,{\rm cm}^{-3})\in[7, 9]$, with a median of 7.6. Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

@@

The large ($>$\,2) virial parameters seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
%
Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
%
This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
%
Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$. On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are more unstable, and \SF may take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.

If most of the MCCs in \flower are stable against collapse, how does it sustain its high SFR of $\sim$70\,\Msun\,yr\pmOne in the starburst phase? Such tension in the interpretation is understood as follows.
%
First, due to energy dissipation on small-scales, such MCCs are no longer supported by turbulence. This in turn would enable
sub-regions of the MCCs to collapse and potentially form OB associations out of these unbound MCCs \citep{Clark04a, Clark05a}.
% Mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential \MM{Gravitational instability is that mechanism (see e.g.\ Wada et al.'s classic review of the subject (2011, doi:10.1017/S1743921311000640), so this isn't really a separate mechanism.} can induce orbit crossing, shocks and dissipation in gas, promoting turbulence dissipation and collapse on smaller scales to trigger \SF. These mechanisms are likely important given high $Q_{\rm eff}$ found across \flower and its few tens of solar masses per year SFR, albeit sporadic.
Further, the SFR of \flower is very bursty and high SFR stages are only transient.
%
Finally, our results are limited by the resolution of the simulation, i.e., in \flower~we do not resolve \SF in {\it cores} and {\it clumps} as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.

@@

The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, after excluding the 
most massive molecular structure identified (which correspond to the main disk of \flower). 
The $\sim$150\,pc-scale structure found with a low density threshold correspond to the main disk of \flower 
and breaks down into smaller MCCs at higher density thresholds, with a typical size of $R\simeq\,50$\,pc.
%
The typical mass of MCCs is $10^{6.5}$\,\Msun. Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc). On the other hand, the gas velocity dispersion 
of $\sigma_{\rm gas}\simeq$\,20-10\,\kms is rather insensitive to the adopted density threshold.

@@

% Toomre:
Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also non-negligible. This illustrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
%
Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates. This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.
%%
%Low-$Q$ sets the regions that fragments 
% and within those regions where alphavir is low enough is where structures to further collapse to form stars.
%
%The MCCs of \flower are more massive and turbulent compared to the Milky Way, with 
% higher gas mass surface densities and velocity dispersions. 
This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
%
%% end
%Determining the multi-phase ISM properties of early galaxies
%is a critical piece to understanding the evolution and
%assembly history of galaxies, since they set the pace
%for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
%While observations leveraging the combination of spatial-spectral imaging of
%multi-band continuum and spectral line emission are crucial,
%% we show in this work that prototypical galaxies at the EoR with properties similar to \flower
%% are expected to have molecular gas structures on sub-kpc scales. 
% Higher resolution imaging of molecular gas 
Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
The Next Generation VLA (ngVLA) in the 2030s could in principle enable imaging of the cold gas down to $\sim$\,200\,pc via \aco line emission. 
% 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
%These predictions can in turn be
%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
%\SF since the cosmic dark ages.

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Jens for useful discussions.
%
TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
% mm
M-MML acknowledges partial support by the NSF through award
AST18-15461, and hospitality from the Insitute for Theoretical
Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.

>>>>

\begin{abstract}
We study the properties of molecular cloud complexes (MCCs) at the Epoch of Reionization (EoR) using cosmological zoom-in simulations.
We identify MCCs in a $z\simeq 6$ prototypical galaxy (``\flower'') 
using an H$_2$ density-based clump finder. 
We compare their mass, size, velocity dispersion, gas surface density, and virial parameter ($\alpha_{\rm vir}$) to \obs.
%
In \flower, the typical MCC mass and size are $10^{6.5}$\,\Msun and $R\simeq45-100$\,pc, 
which are comparable to those found in nearby spirals and starburst galaxies. 
MCCs are highly supersonic and supported by turbulence, with r.m.s velocity dispersions of $\sigma_{\rm gas}\simeq$\,20\,--\,100\,\kms
and pressure of $\log (P/k_B)\simeq$\,7.6\,K\,\cc (i.e., $>$\,1000$\times$ the Milky Way),
similar to those found in nearby and $z$\ssim2 gas-rich starburst galaxies.
%
In addition, we perform stability analysis to understand the origin and dynamical properties of MCCs. We find that MCCs are globally stable in the main disk of \flower. Densest regions where \SF is expected to take place in 
clumps and cores on even smaller scales instead  have lower $\alpha_{\rm vir}$ and Toomre-$Q$ values.
Detailed studies of the star-forming gas dynamics at EoR thus requires a spatial resolution of $\lesssim$40\,pc 
($\simeq$\,0$\farcs$01), which is 
within reach with the Atacama Large (sub-)Millimeter Array (ALMA) and the Next Generation Very Large Array (ngVLA).
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

@@

\subsection{Larson's Relations}\label{sec:PVE}

@@

\subsection{Toomre Stability}\label{sec:Q}

The onset of gravitational instability is tightly connected to \SF
\citep[e.g.,][]{Kennicutt89a, Martin01, Wang94a, Li05b, Li06a}. For axisymmetric modes, the dispersion relation for the growth of density perturbations in a rotating, turbulent disk of finite thickness $h$ is described by
\begin{equation}
\omega^2 = \kappa^2 - \frac{2\pi G \Sigma |k|}{1 + |k| h} + \sigma_{\rm disk}^2 k^2\,,
\label{eqn:3Ddisp}
\end{equation}
where $k$ is the wavenumber and $\kappa$ is the epicyclic frequency, defined as:
\begin{equation}
\kappa^2\equiv\frac{2\Omega}{\altomega}\frac{d}{d\altomega}\left(\altomega^2\Omega\right)\,.
\label{eqn:kappa}
\end{equation}
\citep{Romeo92a},
where $\altomega$ is the galactic radius.
In Equation~\ref{eqn:3Ddisp} the terms on the right hand side are related to rotation, self-gravity and internal pressure, respectively. Heuristically, the instability can be understood by considering the scale at which gravitational potential overcomes the internal energy. Gravity dominates at scales $L > L_J$, where $L_J$ is the Jeans length. However, differential rotation in disk galaxies can stabilize perturbations that might otherwise collapse for $L > L_{\rm rot}$, where $L_{\rm rot}$ is set by $\kappa$. As a result, disks are unstable to gravitational collapse on scales between $L_J < L < L_{\rm rot}$.

@@

\begin{figure*}[htbp]
 \centering
  \includegraphics[width=\textwidth, trim=25 25 35 30, clip]{\figpath/SS_bigfonts/{combined}.pdf}
\caption{
Examples of MCCs identified in \flower by our clump finder.
%
The identified structures (white contour) are superimposed on the map of the mass weighted $H_2$ density field of the galaxy.
%
Two stages of \flower are selected: the accreting phase (left two columns, see \Fig{SFH}a for the definition) and the quiescent phase (right two columns), where \flower display a highly disturbed gas morphology, and a rotating disk configuration, respectively.
%
Panels in the second and fourth columns show the molecular gas distribution projected along different viewing angles. 
%
Different rows show the results obtained by applying different H$_2$ number density cuts $(n_{\rm cut})$, as annotated in each panel.
\label{fig:MCC}
}
\end{figure*}

@@

\subsection{MCC Properties} \label{sec:distribution}

@@

\subsection{MCC Basic Properties} \label{sec:dist}
\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Normalized distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$\eq0.32\,\cc (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels) over all the considered evolutionary stages of \flower traced in the simulation. Note that the scales shown on the $y$-axes are different between the top and bottom panels, as fewer MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

%--------------------------------------------------------------------------
%                                Discussion
%--------------------------------------------------------------------------
\section{Discussion}\label{sec:diss}

\subsection{Synthetic vs Observed MCC Properties} \label{sec:diss1}

@@

The pressure of MCCs identified at the highest $n_{\rm cut}$ ranges in $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressure is comparable to those observed in local ULIRGs; however, the molecular clouds in the latter are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs of \flower are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to the formation (and thus the nature) of these molecular structures.
%
In local ULIRGs, MCCs are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region \citep{Tan00a, Wu18a}. On the other hand, the highly turbulent structures of \flower are the result of extra-planar flows \citep{Kohandel19a} and higher velocity accretion/SN-driven outflows \citep{Gallerani18a}. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

@@

The large virial parameters ($\alpha_{\rm vir}>$\,2) seen in some MCCs of \flower can be understood by first noting that fragmentation {\em can} happen in regions of low $Q$ (if we only consider instability against axisymmetric perturbations), but further evolution and gas collapse depends on the equation of state of the gas.
%
Such fragmentation is expected to take place at the critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$. Second, this fragmentation scale is greater than the typical size of GMCs.
%
This could be interpreted as a result of instability setting the scales for fragmentation, {\em but the truly star-forming regions correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales}.
%
Thus, the high virial parameter found for some MCCs in \flower indicates that they are not the collapsing structures and are found in regions of $Q_{\rm eff}>1$. On the other hand, MCCs in (the denser) regions with a lower Toomre $Q_{\rm eff}$ parameter are more unstable, and \SF may take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates.

@@

High pressure MCCs are found throughout the disk of \flower, with a median pressure of $\bar{P}\simeq10^{7.6}$\,K\,\cc.
This is in contrast to the local ULIRGs, where such high pressure has only been observed in molecular clouds concentrated in their
central regions \citep{Downes98a, Sakamoto08a}. In ULIRGs, MCCs are formed by shock compression and cloud-cloud collisions that 
funnel large amounts of gas from progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}). On the other hand, 
the highly turbulent MCCs of \flower results from extra-planar flows and high velocity accretion/SN-driven outflows. 
The presence of such extra-planar flows may also be the dominant mode for forming the highly supersonic massive 
MCCs observed in gas-rich star-forming galaxies at \z\ssim2, for instance, those reported in \citet{Swinbank11a}.

The sizes of MCCs are only somewhat dependent on the choice of $n_{\rm cut}$, which is a proxy to different tracers used in observations. 
For instance, ......
after excluding the 
most massive molecular structure identified (which correspond to the main disk of \flower). 
The $\sim$150\,pc-scale structure found with a low density threshold correspond to the main disk of \flower 
and breaks down into smaller MCCs at higher density thresholds, with a typical size of $R\simeq\,50$\,pc.
%
The typical mass of MCCs is $10^{6.5}$\,\Msun. Similarly massive molecular structures have been observed in nearby star-forming and starburst galaxies \citep[e.g.,][]{Keto05a, DonovanMeyer13a, Colombo14a, Leroy15a}, and reported in idealized (no stellar feedback) isolated (no cosmological initial conditions) galaxy simulations done at higher resolution (e.g., $l_{\rm cell}\simeq3$\,pc in the 48\,kpc box studied by \citealt{Behrendt16a}). That said, the similar mass range found in MCCs of \flower\ is reassuring --- our results are not far off despite the resolution limit ($l_{\rm cell}\simeq$\,30\,pc). On the other hand, the gas velocity dispersion 
of $\sigma_{\rm gas}\simeq$\,20-10\,\kms is rather insensitive to the adopted density threshold.

@@

% Toomre:
Close resemblance of $Q_{\rm eff}$ and $Q_{\rm star}$ maps indicates that contribution from the stellar component plays an important role in governing the stability of the MCCs against axisymmetric perturbations, especially in the central part of \flower. Similarly, stabilizing effect due to the thickness of its disk is also non-negligible. This illustrates the importance of accounting for stellar contribution and disk thickness when examining the stability of molecular gas structures, especially in relatively evolved and enriched systems at high redshift that are preferentially being observed now.
%
Star formation is expected to take place within its star-forming {\it clumps} and {\it cores} on smaller scales, where energy quickly dissipates. This is consistent with the notion that collapsing structures result from gravitational instability occurring within globally stable structures, which are supported by turbulence and rotation on large scale.
%%
%Low-$Q$ sets the regions that fragments 
% and within those regions where alphavir is low enough is where structures to further collapse to form stars.
%
%The MCCs of \flower are more massive and turbulent compared to the Milky Way, with 
% higher gas mass surface densities and velocity dispersions. 
This also implies that \obs on spatially resolution better than $\simeq$40\,pc are needed to examine the truly star-forming structures (cores), and thus, \SF in the first galaxies.
%
%% end
%Determining the multi-phase ISM properties of early galaxies
%is a critical piece to understanding the evolution and
%assembly history of galaxies, since they set the pace
%for chemical reactions and excitation rates for the coolants in the ISM (and subsequent star formation).
%While observations leveraging the combination of spatial-spectral imaging of
%multi-band continuum and spectral line emission are crucial,
%% we show in this work that prototypical galaxies at the EoR with properties similar to \flower
%% are expected to have molecular gas structures on sub-kpc scales. 
% Higher resolution imaging of molecular gas 
Such resolution is in principle within reach using ALMA, for which 0\farcs01 resolution images can be attained using the high frequency bands. 
The Next Generation VLA (ngVLA) in the 2030s will enable imaging of molecular gas down to $\sim$\,200\,pc \citep{Casey18a} blah blah blah \DL{editing}.
% 0.005" highest freq; ~0.05 for 16 GHz; CO10 for z~6
On the other hand, cosmological zoom-in simulations, such as \ncode{Serra}, while inherently limited in galaxy statistics and are subject to the sub-grid models adopted, serve as a useful tool for examining and making predictions on the morphology and dynamics of the molecular ISM of the first galaxies.
%These predictions can in turn be
%tested with high resolution imaging of the gas content in the first galaxies with telescopes such as ALMA and the ngVLA, thereby
%enabling us to test our findings and refine future simulations to shed light on the physical processes behind
%\SF since the cosmic dark ages.

@@

\section*{Acknowledgements}
We thank Jens Kauffmann, Thushara Pillai, and Mark Swinbank for sharing their data, and Caitlin Casey for useful discussions.
%
TKDL gratefully acknowledges support by the NSF through award SOSPA4-009 from the NRAO and support from the Simons Foundation.
%
AF acknowledges support from the ERC Advanced Grant INTERSTELLAR
H2020/740120.
% mm
M-MML acknowledges partial support by the NSF through award
AST18-15461, and hospitality from the Insitute for Theoretical
Astrophysics at the University of Heidleberg.
%
This work is based on a project developed at the Kavli Summer Program in Astrophysics (KSPA) held at the Center for Computational Astrophysics of the Flatiron Institute in 2018. The program was co-funded by the Kavli Foundation and the Simons Foundation.
%
We thank the KSPA Scientific and Local Organizing Committees, and the program founder, Pascale Garaud, for supporting the genesis of this work.
%
We also thank the Center for Cosmology and Particle Physics at the New York University for their hospitality in hosting us after the steam pipe explosion in NYC during the KSPA.
%
This research has made use of NASA's Astrophysics Data System Bibliographic Services.
%
We acknowledge use of the Python programming language \citep{VanRossum1991}, Astropy \citep{astropy}, Cython \citep{behnel2010cython}, Matplotlib \citep{Hunter2007}, NumPy \citep{VanDerWalt2011}, \ncode{Pymses} \citep{Labadens2012}, SciPy \citep{scipyref}, and \ncode{yt} \citep{Smith09a,Turk11a}.
%
%and \ncode{yt}, a community-developed Python package for analyzing simulation data in Astronomy.
